Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-06-10 manuscripts/TCS2023/tcs2023.tex
Update scheme

A state \(v \in \mathbb{B}^{n}\) is as a mapping \(v \colon V \mapsto \mathbb{B}\) that assigns either 0 (inactive) or 1 (active) to each node.
We denote the set of all possible states of a Boolean network \(\mathcal{N}\) by \(\mathcal{S}_{\mathcal{N}} = \mathbb{B}^n\).
At each time step \(t\), node \(v_i\) can, depending on the update scheme, update its state by
\[v_i(t + 1) =
  \begin{cases}
    &f_i(v(t))\\
    \text{or} &v_i(t)
  \end{cases}
\]
where \(v(t)\) (resp. \(v_i(t)\)) is the state of \(\mathcal{N}\) (resp. the state of node \(v_i\)) at time \(t\).
Note that for simplicity, we write \(f_i(v(t))\) even if \(\IN(v_i) \subsetneq V\) (i.e., \(\IN(v_i)\) does not contain some nodes of \(V\)).
An update scheme of a Boolean network specifies which nodes update their states, as defined above, through time evolution~\cite{thomas1991regulatory}.
Following the update scheme, the Boolean network transits from a state to another state (possibly identical).
This transition is called the \emph{state transition} and denoted by \(\rightarrow \subseteq \mathcal{S}_{\mathcal{N}} \times \mathcal{S}_{\mathcal{N}}\).
Then the dynamics of \(\mathcal{N}\) is captured by the directed graph \((\mathcal{S}_{\mathcal{N}}, \rightarrow)\) called the State Transition Graph (STG).
There are many different update schemes, but the two main types~\cite{thomas1991regulatory} are: \emph{synchronous}, where all the nodes are \change{updated} simultaneously, and \emph{fully asynchronous}, where only one node is selected non-deterministically to be updated.

>>>>

\change{A state \(s \in \mathbb{B}^{n}\) is as a mapping \(s \colon V \mapsto \mathbb{B}\) that assigns either 0 (inactive) or 1 (active) to each node.}
We denote the set of all possible states of a Boolean network \(\mathcal{N}\) by \(\mathcal{S}_{\mathcal{N}} = \mathbb{B}^n\).
\change{At each time step \(t\), node \(v_i\) can update its state by
\[s'(v_i) = f_i(s)
\]
where \(s\) (resp. \(s'\)) is the state of \(\mathcal{N}\) at time \(t\) (resp. \(t + 1\)).
Note that for simplicity, we write \(f_i(s)\) even if \(\IN(v_i) \subsetneq V\) (i.e., \(\IN(v_i)\) does not contain some nodes of \(V\)).
An update scheme of a Boolean network specifies the way that the nodes update their states through time evolution~\cite{gershenson2004introduction}.
There are many different update schemes, but the two main types~\cite{gershenson2004introduction} are: \emph{synchronous}, where all the nodes are \change{updated} simultaneously, and \emph{fully asynchronous}, where only one node is selected non-deterministically to be updated.}
Following the update scheme, the Boolean network transits from a state to another state (possibly identical).
This transition is called the \emph{state transition} and denoted by \(\rightarrow \subseteq \mathcal{S}_{\mathcal{N}} \times \mathcal{S}_{\mathcal{N}}\).
\change{For example, under the synchronous update scheme, we have \(x \rightarrow y\) if and only if \(y(v_i) = f_i(x), \forall v_i \in V\), whereas under the fully asynchronous update scheme, we have \(x \rightarrow y\) if and only if there is a node \(v_i \in V\) such that \(y(v_i) = f_i(x)\) and \(y(v_j) = x(v_j), \forall v_j \in V, j \neq i\).}
Then the dynamics of \(\mathcal{N}\) is captured by the directed graph \((\mathcal{S}_{\mathcal{N}}, \rightarrow)\) called the State Transition Graph (STG).
